---
title: "ManjeetPanda_Aug_SVAP_Asmt_R2"
author: "Manjeet Panda"
date: "October 8, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
```

```{r}
setwd("C:/Users/sg0949286/Documents/R/WorkSpace/SVAP")
library(plyr)
library(rvest)
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(prophet)
library(tm)
library(SnowballC)
library(wordcloud)
library(mice)
library(VIM)
library(tidyr)
library(pracma)
library(scales)
library(forecast)
```

##Frame the question:
1. What are the different crops being grown in Odisha?
2. What are the top crops grown in Odisha in each season in 2015?
3. What is the most grown crop in Odisha?
4. What could be predicted produce of the most grown crop in Odisha in 2016?

Before that let's have a look at the structure and some of the snapshots of the raw data that we have.
```{r}
#Acquire Data
getwd()
raw_data <- read.csv("apy.csv", header = TRUE)
str(raw_data)
head(raw_data)
tail(raw_data)
raw_data$State_Name <- as.character(raw_data$State_Name)
raw_data$District_Name <- as.character(raw_data$District_Name)
raw_data$Season <- as.character(raw_data$Season)
raw_data$Crop <- as.character(raw_data$Crop)
raw_data$Season <-  gsub(" ",'',raw_data$Season)
```

Now, the crops being grown in Odisha are,
```{r}
raw_data_odisha = raw_data %>% filter(raw_data$State_Name == "Odisha")
wordcloud(raw_data_odisha$Crop, max.words = 150, random.order = FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))
```

#Check for missing values (Data Refinement)
```{r}
md.pattern(raw_data_odisha)
missing.values <- aggr(raw_data_odisha, col=c('navyblue','yellow'),
                       numbers=TRUE, sortVars=TRUE,
                       labels=names(raw_data_odisha), cex.axis=.7,
                       gap=1, ylab=c("Missing data","Pattern"))
```
From the above plot, we infer that The missing values are only present in Production values and since they are only 0.038% of the total values, we will ignore all the missing values.

```{r}
raw_data_odisha <- raw_data_odisha %>%  filter(!is.na(raw_data_odisha$State_Name))
raw_data_odisha <- raw_data_odisha %>%  filter(!is.na(raw_data_odisha$District_Name))
raw_data_odisha <- raw_data_odisha %>%  filter(!is.na(raw_data_odisha$Crop_Year))
raw_data_odisha <- raw_data_odisha %>%  filter(!is.na(raw_data_odisha$Season))
raw_data_odisha <- raw_data_odisha %>%  filter(!is.na(raw_data_odisha$Crop))
raw_data_odisha <- raw_data_odisha %>%  filter(!is.na(raw_data_odisha$Area))
processed_data_odisha_NotNull <- raw_data_odisha %>% filter(!is.na(raw_data_odisha$Production))
```

After missing value treatment, let's verify if there are any more missing values
```{r}
missing.values <- aggr(processed_data_odisha_NotNull, col=c('navyblue','yellow'),
                       numbers=TRUE, sortVars=TRUE,
                       labels=names(processed_data_odisha_NotNull), cex.axis=.7,
                       gap=1, ylab=c("Missing data","Pattern"))
```

from the graph it is clear that there are no more missing data.


#What were the season wise top crops grown in Odisha in 2015?
```{r}
#Data Transformation and exploration
processed_data_by_season <- aggregate(Production ~ (Crop_Year + Season + Crop),
                                      data=processed_data_odisha_NotNull,
                                      FUN=sum)
processed_data_by_season_2015 <- processed_data_by_season %>%
                                 filter(processed_data_by_season$Crop_Year == 2015)
processed_data_by_season_2015 %>% 
  group_by(Crop) %>%
  arrange(desc(Production)) %>%
  head(15) %>%
  ggplot(aes(reorder(Crop, Production), Production, fill=Crop)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~Season)
```


From the above figure we conclude that Rice was the most widely produced crop in Odisha across seasons in 2015.

#What is the forecast of rice production in 2016?
We will create a timeseries and make forecasts using simple exponential smoothing and use Holt-Winters exponential smoothing for the same.
```{r}
#Model and Insight
processed_data_Rice <- processed_data_odisha_NotNull %>%
                       filter(processed_data_odisha_NotNull$Crop == "Rice")
processed_data_year <- aggregate(Production ~ Crop_Year,
                                      data=processed_data_Rice,
                                      FUN=sum)
time_series_temp <- processed_data_year %>%
  mutate(date = paste("01","01",Crop_Year, sep = "-"))

time_series <- time_series_temp[,-1]
time_series <- time_series %>% select(date, Production)
time_series$date <- as.Date(x = time_series$date, format = "%d-%m-%Y")
time_series.Production <- as.ts(time_series$Production, start = c(1998,1), frequency = 12)
plot.ts(time_series.Production)
```
The above graph shows us the annual trend of rice production in strating from 1998 till 2015.

Now, the forecasting of rice production in coming years.
```{r}
#Communicate
time_series.Production.Forecasts <- HoltWinters(time_series.Production, beta=FALSE, gamma=FALSE)
plot(forecast(time_series.Production.Forecasts))

```

From the above plot, we can conclude that the rice production in 2016 will be 7000000 units with 80% prediction area between 5000000 units to 9000000 units and 95% prediction area between 4000000 units to 10000000 units.

